%-------------------------
% Resume in Latex for Hassan Mikawi
% Adapted from template and design considerations inspired by Mostafa Adel El Sawy
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Page setup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeEducationHeading}[6]{\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

% Resume starts here
\begin{document}

% Heading
\begin{center}
    \textbf{\Huge \scshape Hassan Mikawi} \\ \vspace{3pt}
    \small 
    \faMobile \hspace{.5pt} \href{tel:+201023667216}{+201023667216} $|$
    \faEnvelope \hspace{.5pt} \href{mailto:hassansherif122202@gmail.com}{hassansherif122202@gmail.com
} $|$
    \faLinkedin \hspace{.5pt} \href{https://www.linkedin.com/in/hassan-sherif-1314b9238}{LinkedIn} $|$
    \faGithub \hspace{.5pt} \href{https://github.com/Hassan220022}{GitHub} $|$
    \hspace{.5pt} {Fifth Settlement, New Cairo}
\end{center}

% Education - Updated Section with GPA and IGCSE Achievement
\section{Education}
\resumeSubHeadingListStart
    \resumeEducationHeading
<<<<<<< HEAD
      {Boğaziçi University
      % \normalfont{(Admission rate: 0.09\%)}
      }{Istanbul, Turkey}
      {B.Sc. in Electrical and Electronics Engineering;   \textbf{GPA: 3.62/4.00}}{Sep 2018 \textbf{--} Jun 2023}
      {Minor Degree in Computer Science;
      \textbf{GPA: 3.58/4.00}}{Oct 2020 \textbf{--} Jun 2023}
        \resumeSubHeadingListStart
        \small{\item{
            % \textbf{Relevant coursework:} Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision
            \textbf{National University Admission Exam (YKS):} Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)}}
        \resumeSubHeadingListEnd
    
    % \resumeSubheading
      % {Kocaeli Science High School
      % \normalfont{(Admission rate: 0.85\%)}
      % }{Kocaeli, Turkey}
      % {High School Diploma;   \textbf{GPA: 97.03/100}}{Sep 2014 \textbf{--} Jun 2018}
    
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ C/C++, C\#, Java, Python, Go, JavaScript, TypeScript, SQL, Swift, Scala, MATLAB, R} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Qt, Flask, Django, Node.js, React.js, MySQL, MongoDB, Git, SVN, Docker, AWS, Kubernetes, GCP, Kafka, RabbitMQ, OpenCV, PyTorch, TensorFlow} \\ \vspace{3pt}
        
        \textbf{Methodologies:}{ Agile, Scrum, OOP, Functional Programming, DevOps, CI/CD, TDD} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------
=======
      {Arab Academy For Science Technology \& Maritime Transport (AASTMT)}{Expected Graduation: 2025}
      {Bachelor of Science in Computer Engineering; \textbf{GPA: 3.2/4.0}}{}{}{}
    \resumeSubheading
      {International General Certificate of Secondary Education (IGCSE)}{}
      {Cumulative Score: 98\% (with factor), 100\% (without factor)}{}{}
\resumeSubHeadingListEnd
>>>>>>> refs/remotes/origin/main

% Experience - Continued
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
<<<<<<< HEAD
      {Avikon}{Istanbul, Turkey}
      {Software Engineer}{Dec 2023 \textbf{--} Present, Full-time}
        \resumeItemListStart
            \resumeItem{Designed a Qt-based chat application utilizing TCP for real-time communication within a client-server architecture, demonstrating expertise in socket programming, data serialization, and message routing.}
            \resumeItem{Crafted message types in IDL and designed a data-centric publish-subscribe architecture based on a flyweight design pattern to implement OpenDDS for a radar system's command and control interface. Utilized QoS policies to facilitate the transmission of both volatile and persistent data across different topics.}
            \resumeItem{Implemented a fully asynchronous AMQP-based C++ client with a layered architecture for RabbitMQ message broker to ensure seamless message handling among multiple topics.}
            \resumeItem{Developed a cross-platform asynchronous program to refine UAV detection for a GIS application. Benchmarked point-in-polygon algorithms with a GeoJSON polygon database concurrently fetched from MongoDB.}
        \resumeItemListEnd

=======
      {Co-founder and CTO at YBM}{}
      {Oversaw the technical direction, managed website development, and various digital projects.}{}{}\\
>>>>>>> refs/remotes/origin/main
    \resumeSubheading
      {Intern at Arab Organization for Industrialization (AOI)}{}{Contributed to the manufacturing line for hardware components, offering technical guidance and support to the assembly process.}{}
\resumeSubHeadingListEnd

<<<<<<< HEAD
    % \resumeSubheading
      % {Scale AI}{San Francisco, California, United States (Remote)}
      % {Prompt Engineer}{Mar 2023 \textbf{--} Sep 2023, Freelance}
        % \resumeItemListStart
            % \resumeItem{Crafted elaborate Turkish prompts for various generative AI tasks. Tailored prompts using well-defined formats such as natural language questions and structured inputs based on the task's domain to fine-tune the LLM, improving the chatbot's responses and enhancing overall performance.}
            % \resumeItem{Provided user feedback by reviewing and scoring the chatbot's responses to ensure they align with intended chatbot behaviors and the chatbot produces accurate and contextually appropriate responses to given prompts.}
            % \resumeItem{Engaged in collaborative meetings with cross-functional teams and project coordinators, actively seeking guidance, addressing queries, and collectively brainstorming strategies to generate higher-quality prompts.}
        % \resumeItemListEnd

    \resumeSubheading
      {Max Planck Institute for Intelligent Systems}{Stuttgart, Baden\textbf{-}Württemberg, Germany}
      {Undergraduate Researcher}{Jun 2022 \textbf{--} Aug 2022, Internship}
        \resumeItemListStart
            \resumeItem{Engaged in collaborative research within the Robotics, Collectives and Learning subgroup at the Physical Intelligence Department with Ph.D. students \href{https://www.linkedin.com/in/sinan-ozgun-demir-981311129/}{\color{blue}Sinan Özgün Demir} and \href{https://www.linkedin.com/in/alpkaracakol/}{\color{blue}Alp Can Karacakol} on a project about 3D printing and heat-assisted magnetic programming of soft machines under the supervision of \href{https://www.linkedin.com/in/metin-sitti-0a8a712/}{\color{blue}Prof. Dr. Metin Sitti}.}
            \resumeItem{Optimized a C++ ROS package for real-time conversion of 3D motion controller events to ROS messages, achieving high-frequency and buffer-free synchronization.}
            \resumeItem{Developed an Arduino Mega driver to activate a laser and pressure regulator, for monitoring coil temperatures and PID tuning to control the coil currents. Established a robust ROS-Arduino communication network by integrating ROSSerial and handshaking to simulate a 3D printing and magnetic programming process with Python.}
            % \resumeItem{Designed the project's system and software architecture, flowchart, and state machine diagram. Expanded G-code capabilities by incorporating spherical coordinates to specify the direction of magnetization for shape morphing.}
        \resumeItemListEnd
    
    % \resumeSubheading
      % {Nanonetworking Research Group, Boğaziçi University}{Istanbul, Turkey}
      % {Undergraduate Researcher}{Oct 2021 \textbf{--} Jun 2022, Part-time}
        % \resumeItemListStart
            % \resumeItem{Worked on the “Design and Implementation of Molecular Communication Systems Using Index Modulation” project under the supervision of \href{https://www.linkedin.com/in/alipusane/}{\color{blue}Prof. Dr. Ali Emre Pusane}.}
            % \resumeItem{Simulated the Brownian motion of molecules in a SISO MCvD system and predicted simulation parameters such as receiver radius, diffusion coefficient, and transmitter-receiver distance using CNNs with Keras and TensorFlow.}
            % \resumeItem{Plotted the arrival of molecules per symbol duration in a SISO MCvD system using Binomial, Poisson, and Gaussian model approximations with MATLAB.}
            % \resumeItem{Ran Monte Carlo simulations of the Gaussian model to encode and decode randomized binary sequences in a SISO MCvD system using BCSK modulation technique and calculated the bit error rate on Z-channel.}
        % \resumeItemListEnd

    % \vspace{20pt}
    \resumeSubheading
      {SESTEK Speech Enabled Software Technologies}{Istanbul, Turkey}
      {AI Research and Development Intern}{Jan 2022 \textbf{--} Feb 2022, Internship}
        \resumeItemListStart
            % \resumeItem{Executed diverse NLP tasks, including NER, POS tagging, sentiment analysis, text classification, and extractive and generative QA using transformers and Hugging Face libraries. Conducted a thorough literature review on information retrieval and reading comprehension to stay updated on SOTA ML models.}
            \resumeItem{Developed a generative QA system with dense passage retrieval (DPR) and retrieval-augmented generation (RAG) techniques using the Haystack framework and PyTorch.}
            \resumeItem{Worked on a Turkish open-domain QA system made by fine-tuning BERTurk and XLM-Roberta models. Tabularized exact match and F1 scores derived from DeepMind's XQuAD and various Turkish data sets.}
        \resumeItemListEnd

    % \resumeSubheading
      % {Meteksan Defense Industry Inc.}{Ankara, Turkey}
      % {Analog Design Engineering Intern}{Jul 2021 \textbf{--} Aug 2021, Internship}
        % \resumeItemListStart
            % \resumeItem{Designed and simulated numerous analog circuits such as voltage-mode controlled buck converter, phase-shifted full-bridge isolated DC-DC converter, and EMI filters with LTspice. Integrated these circuits and implemented a 320 W power distribution unit to be used in a radar system's power circuit board.}
            % \resumeItem{Researched real-world compatible electronic components to be used in such circuits including GaNFETs, high-side gate drivers, and Schottky diodes.}
            % \resumeItem{Assembled PCBs of both common and differential mode filters and used VNA Bode 100 to measure the cut-off frequencies.}
        % \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
=======
% Skills
\section{Skills}
\resumeSubHeadingListStart
>>>>>>> refs/remotes/origin/main
    \small{\item{
        \textbf{Languages:} C, C++, Python, Java, C\# \\
        \textbf{Mobile App Development:} Flutter (Learning)\\
        \textbf{Operating Systems:} Windows, Linux, macOS \\
        \textbf{Methodologies:}{ Agile , OOP, Functional Programming, DevOps}
}
\resumeSubHeadingListEnd

% Projects - Updated Section with Flutter XO Game and Removed C version
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Weapons Detection in Video}}{AI}\\
              \resumeItem{Developed an AI model for real-time detection of weapons in video streams, employing the \textbf{YOLOv8} object detection\\ algorithm. Focused on optimizing detection precision, significantly reducing false positives through machine learning techniques. Achieved enhanced model performance with improved detection accuracy and processing speed on a diverse dataset.}
    \resumeProjectHeading
          {\textbf{Tic-Tac-Toe Game}}{Flutter}
          \resumeItem{Engineered a cross-platform Tic Tac Toe game with Flutter, featuring an intuitive UI and multiplayer functionality over the network.\\}
    \resumeProjectHeading
          {\textbf{Home Server}}{Linux}
          \resumeItem{Configured a versatile home server for media storage and gaming, enhancing overall performance and security.}
    \resumeProjectHeading
          {\textbf{Morse Code Decoder App}}{Python}
          \resumeItem{Crafted an intuitive Morse code decoder application utilizing PyQt and PyAudio, focusing on user-friendly design and efficiency.}
    \resumeProjectHeading
          {\textbf{Hyper Market Management System}}{Java}
          \resumeItem{Constructed a comprehensive management system for hypermarkets, featuring modular design for administration, inventory, and sales processes.}
    \resumeProjectHeading
          {\textbf{MIPS Processor}}{VHDL}
          \resumeItem{Implemented a MIPS processor simulation in VHDL, encapsulating core functionalities including PC, ALU, and data memory management.}
    \resumeProjectHeading
          {\textbf{Infix to Postfix Calculator}}{C++}
          \resumeItem{Developed a calculator for converting and evaluating infix to postfix mathematical expressions, demonstrating proficiency in C++.}
    \resumeProjectHeading
          {\textbf{SIC and Assembly Compiler}}{C}
          \resumeItem{Created a compiler for SIC/XE machine language, showcasing deep understanding of assembly language and compiler construction.}
\resumeSubHeadingListEnd


% Experience - Updated Section with Club Involvement
\section{Leadership \& Extracurricular Activities}
\resumeSubHeadingListStart
    \resumeSubheading
      {President of Inseptum Club}{AASTMT}
      {Lead initiatives to bridge the gap between corporate life and student experience, arranging HR sessions, internships, and facilitating student adaptability to corporate environments.}{}{}\\
    \resumeSubheading
      {AI Benefits \& Python Tutoring}{AASTMT}
      {Engaged in AI club activities; conducted Python courses for younger students, and organized complex tournaments to promote practical learning and application of AI.}{}{}
\resumeSubHeadingListEnd



% Re-arrange sections if necessary to fit the new content appropriately


% Footer
\begin{center}
    \small Last Updated: \today
\end{center}

<<<<<<< HEAD
%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
=======
\end{document}

>>>>>>> refs/remotes/origin/main
