\documentclass[11pt, a4paper]{moderncv}
\moderncvstyle{banking} % Style options: 'casual' (default), 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue} % Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'
\usepackage[scale=0.75]{geometry} % Adjust the page margins
\usepackage{fontawesome}

% Personal Information
\name{Hassan}{Mikawi}
\phone[mobile]{+201023667216}
\email{hassansherif122202@gmail.com}
\social[linkedin]{hassan-sherif-1314b9238}
\social[github]{Hassan220022}
\address{Fifth Settlement, New Cairo}

%----------------------------------------------------------------------------------
%            Content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\vspace{-10mm} % Reduce space after title

\section{Education}
\cventry{2020--2025}{Bachelor of Science in Computer Engineering}{Arab Academy For Science Technology \& Maritime Transport (AASTMT)}{Cairo, Egypt}{\textit{GPA: 3.2/4.0}}{Specialization in Software Engineering.}
\cventry{Year}{IGCSE}{High School}{Sakkara language school}{\textit{98\% with factor, 100\% without factor}}{}

\section{Experience}
\cventry{Year--Year}{Co-founder and CTO}{YBM}{Cairo, Egypt}{}{Oversaw technical direction and managed the development of the company's digital presence including website and database management.}
\cventry{Summer 2023}{Intern}{Arab Organization for Industrialization}{Cairo, Egypt}{}{Assisted in the manufacturing line for hardware components, offering technical guidance and improved assembly processes.}
\cventry{Year--Year}{President}{Inseptum Club}{AASTMT}{}{Bridged the gap between corporate life and students by arranging HR sessions, internships, and aiding students in adapting to corporate environments.}

\section{Projects}
\cvitem{YOLOv8 Weapon Detection}{Developed an AI model for real-time weapons detection in video streams, employing advanced machine learning techniques for optimization.}
\cvitem{Tic Tac Toe Game (Flutter)}{Implemented a cross-platform multiplayer game using Flutter, showcasing strong UI/UX design and network programming.}
\cvitem{Simple Shell}{Designed and implemented a Unix-like shell in C, demonstrating deep understanding of system calls and process management.}
\cvitem{Hyper Market Management System}{Designed and implemented a Unix-like shell in C, demonstrating deep understanding of system calls and process management.}

\section{Skills}
\cvitem{Programming Languages}{C, C++, Python, Java, C\#}
\cvitem{Technologies}{Flutter, Docker, Linux, Git}
\cvitem{Frameworks}{Machine Learning, Computer Vision with YOLOv8, Backend Development}
\cvitem{Soft Skills}{Leadership, Problem-solving, Teamwork, Communication}

\section{Certifications and Ongoing Education}
\cvitem{Software Engineering with ALX}{Currently enrolled in an intensive Software Engineering course covering Agile methodologies, version control, CI/CD pipelines, and modern software development practices. Expected completion in September 2024.}
\cvitem{Embedded Systems}{Completed a hands-on embedded systems course at IMT, focusing on microcontroller programming and interfacing.}

\end{document}
