\documentclass[a4, 10pt]{article}
%Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Hassan Sherif Mikawi} \\ \vspace{5pt}
    \small
    \hspace{.5pt} \href{tel:+201023667216}{+201023667216}
    $|$
    \hspace{.5pt} \href{mailto:hassansherif122202@gmail.com}{hassansherif122202@gmail.com}
    $|$
    \hspace{.5pt} \href{https://www.linkedin.com/in/mikawi}{linkedin.com/in/mikawi}
    $|$
    \hspace{.5pt} \href{https://github.com/Hassan220022}{github}
    $|$
     \hspace{.5pt} \href{https://mikawi.org}{Portfolio}
\end{center}




%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.linkedin.com/company/orange-egypt/}{Orange Egypt}}{Cairo, Egypt}
      {Software Engineer – Power \& Operation Team}{Jan 2026 \textbf{--} Present}
        \resumeItemListStart
          \resumeItem{Sole software engineer on the Power \& Operation team, responsible for architecting and delivering an end-to-end enterprise platform that centralises battery health analysis, alarm monitoring, and performance testing across \textbf{10,500+ telecom sites} nationwide.}
          \resumeItem{Engineered the complete solution from scratch: RESTful backend (FastAPI), relational database, JWT-based authentication, scheduled cron jobs, SMTP email notifications, and role-based analytical dashboards — with no dedicated DevOps or infrastructure team.}
          \resumeItem{Reduced repetitive manual workflows for the operations team by \textbf{40\%} through automated data pipelines, intelligent alerting, and centralised reporting, replacing fragmented and time-intensive processes.}
          \resumeItem{Drive all architectural decisions independently — identifying system weak points, iterating rapidly, and keeping the platform stable while it remains in active production development.}
        \resumeItemListEnd

    \resumeSubheading
      {Game Spot}{Cairo, Egypt}
      {Co-Founder \& Sole Software Engineer / Architect}{2025 \textbf{--} Present}
        \resumeItemListStart
          \resumeItem{Co-founded Game Spot and serve as the entire engineering department for a SaaS platform and mobile application that connects players with real-world gaming venues (PS cafés, billiards clubs, ping-pong halls, etc.) through a real-time, two-sided marketplace.}
          \resumeItem{Designed and built the full product stack: a FastAPI/Python backend with Postgres/Supabase, a consumer-facing mobile app (Flutter/Expo/React Native), and a Next.js Provider Portal for venue owners to manage listings, bookings, calendars, tournaments, and revenue.}
          \resumeItem{Integrated Paymob and Stripe for payment processing and Apple Wallet for digital check-in passes; deployed across Cloudflare, Vercel, and Railway with CI/CD pipelines — serving active venues and live bookings in production.}
          \resumeItem{Own every technical trade-off and product direction decision, directly shaping the platform's architecture, feature roadmap, and scalability strategy toward becoming the default gaming-venue discovery and booking channel in Egypt.}
        \resumeItemListEnd

    \resumeSubheading
      {Al-Ahram Establishment}{Cairo, Egypt}
      {Software Engineer Intern}{Sep 2024 \textbf{--} Dec 2024}
        \resumeItemListStart
          \resumeItem{Automated data extraction from Microsoft SQL Server using Python, reducing manual reporting overhead for senior developers and increasing reliability of core reporting workflows.}
          \resumeItem{Delivered a production-ready agricultural web application end-to-end, taking ownership of both backend services and frontend experience to satisfy stakeholder requirements.}
          \resumeItem{Improved platform robustness and performance by hardening security, managing on-premise deployment, and optimizing request handling under load for day-to-day internal use.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {\href{https://aast.edu/en/index.php?from=edurank.org}{Arab Academy for Science, Technology and Maritime Transport (AAST)}}{Cairo, Egypt}
      {B.Sc. in Electrical and Computer Engineering\textbf{ GPA: 3.3/4.00}}{Oct 2020 \textbf{--} July 2025}
      
    % \resumeSubheading
    % {\href{https://tech.alxafrica.com/hubfs/ALX-Software-Engineering-Curriculum.pdf?hsLang=en}{ALX Software Engineering}}{Cairo, Egypt}
    % {Comprehensive full stack development course}{Apr 2023 \textbf{--} May 2024}
    
  \resumeSubHeadingListEnd
%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{\href{https://toddlerwear.net}{ToddlerWear – Kids E-Commerce Platform}} $|$ {Next.js, TypeScript, Convex, Cloudflare, Paymob}}
  {Jan 2026}
\resumeItemListStart
        \resumeItem{Delivered a production-ready, mobile-optimized e-commerce platform for kids fashion using Next.js 15 and Convex, tailored to the Egyptian market with localized currency, address formats, and payment options.}
        \resumeItem{Designed and shipped a rich customer journey including smart search, advanced catalog filtering, persistent cart and wishlist, detailed size guides, user accounts, guest checkout, product reviews, and real-time order tracking.}
        \resumeItem{Owned the operational backbone of the store by building an admin console for non-technical staff (products, inventory, bulk CSV imports, orders and returns, homepage and static content, role-based access) and integrating Paymob and Cloudflare (Workers, R2) with secure webhooks, HMAC validation, and reliable email notifications via Resend.}

    
\resumeItemListEnd


    
\resumeProjectHeading
  {\textbf{\href{https://g2scv.live}{G2scv – AI-Powered CV Builder (Co‑Founder / Core Developer)}} $|$ {FastAPI, Flutter}}
  {July 2025 - Present}

          \resumeItemListStart
          
            \resumeItem{Co‑founded and led development of g2scv, an AI-powered CV builder that turns developers’ GitHub, LinkedIn, and existing resumes into tailored, ATS-friendly profiles for specific roles.}
            \resumeItem{Built robust integrations with GitHub and LinkedIn to automatically surface relevant projects, skills, and experience, feeding them into an AI pipeline for targeted CV generation.}
            \resumeItem{Collaborated on the design of AI prompting and retrieval flows to improve clarity and impact of CV bullet points, while keeping content faithful to the candidate’s real background.}
            \resumeItem{Contributed to a privacy-focused product architecture and tiered subscription offering, balancing individual users’ needs with advanced features for power users and teams.}


          \resumeItemListEnd
       {\vspace{3pt}\textbf{\href{https://github.com/Flex-Language}{Flex Programming Language (Grade Project)}}
        $|$
          {Python, Web, Ai agentic cli, VSCode Extension}}{Jan 2024 -- July 2025}
        \resumeItemListStart
        \resumeItem{Conceived and delivered Flex, an AI-assisted universal programming language with multi-syntax support (English, Franco‑Arabic transliteration, and C‑style) to make programming more accessible for Arabic-speaking developers and beginners.}
        \resumeItem{Implemented the full interpreter in Python, including a regex-based lexer, recursive descent parser, AST evaluator, and robust runtime error handling with human-readable AI explanations in the terminal.}
        \resumeItem{Shipped a web-based IDE and VS Code extensions with real-time code execution, language tooling, and an integrated chatbot, plus a modular import system and cross-platform executables for Windows, macOS, and Linux.}
            
            % \resumeItem{Created a feature-rich online IDE with real-time input handling and code execution capabilities}
            % \resumeItem{Built two VSCode extensions: one for language support and another with an integrated chatbot to facilitate learning for students}
            % \resumeItem{Implemented cross-platform compatibility with executable builds for Windows, macOS, and Linux}
            % \resumeItem{Designed a smart import system supporting modular code organization and library management}
        \resumeItemListEnd
      % \resumeProjectHeading
      %   {\textbf{ALX-Portfolio-Project}
      %   $|$
      %     {Node.js, MongoDB, JavaScript, React}}{2024}
      %     \resumeItemListStart
      %       \resumeItem{Engineered a Node.js backend API to ingest and expose global COVID-19 statistics from public datasets}
      %       \resumeItem{Implemented MongoDB for persisting time-series data and snapshot statistics}
      %       \resumeItem{Created a React frontend with Mapbox integration to visualize geospatial data}
      %     \resumeItemListEnd

      % \resumeProjectHeading
      %   {\textbf{Fekra}
      %   $|$
      %     {Dart, Supabase, OpenAI Whisper, Flutter}}{2024}
      %     \resumeItemListStart
      %       \resumeItem{Integrated Supabase as a backend-as-a-service to handle secure authentication (OAuth) and cloud data sync}
      %       \resumeItem{Implemented OpenAI Whisper API for voice-to-text transcription features}
      %       \resumeItem{Designed a production-oriented architecture with clear separation of concerns}
      %     \resumeItemListEnd

      % \resumeProjectHeading
      %   {\href{https://github.com/Hassan220022/Hyper-Market-Management-System}{\textbf{Hyper Market Management System}}
      %   $|$
      %     {Java, MySQL, NetBeans, jBCrypt, FlatLaf}}{Jun 2023}
      %     \resumeItemListStart
      %       \resumeItem{Revolutionized market management with a comprehensive system for sales, purchases, and employee roles}
      %       \resumeItem{Implemented administrative, marketing, inventory management, sales, and user modules}
      %       \resumeItem{Used Java for backend development, NetBeans for GUI, and MySQL for the database}
      %       \resumeItem{Enhanced security with password management using jBCrypt and improved design using FlatLaf}
      %       \resumeItem{Packaged for easy installation using jpackage with an executable installer available in the releases}
      %     \resumeItemListEnd

      % \resumeProjectHeading
      %   {\href{https://github.com/Hassan220022/simple_shell}{\textbf{Simple Shell}}
      %   $|$
      %     {C, Unix System Calls, GCC, Betty Coding Style}}{Dec 2023}
      %     \resumeItemListStart
      %       \resumeItem{Developed a UNIX command line interpreter as a group project, emulating basic shell functionalities}
      %       \resumeItem{Implemented functionalities including command execution, environment manipulation, and custom input handling}
      %       \resumeItem{Incorporated system-level programming with Unix system calls like fork, execve, and waitpid to manage processes}
      %       \resumeItem{Utilized C for core development with strict adherence to the Betty coding style for clean and maintainable code}
      %     \resumeItemListEnd

    \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK & CERTIFICATIONS -----------

\section{Relevant Coursework \& Certifications}
  \resumeSubHeadingListStart
    % \resumeItem{\textbf{Networking \& Cyber Security Internship at \href{https://seegypt.com/}{SEE Company}:} Learned cyber security concepts and CCNA fundamentals through practical training.}
    % \resumeItem{\textbf{Flutter Development Course on \href{https://www.udemy.com/share/101rfI3@KrQXcIQfUCfZKdb0xVqKLKdnx6689mXcLDpKdRQCCB3qYZEyTs9KuzFftgd7fqvAJA==/}{Udemy}:} Built multiple projects: "Acade" game (XO, Hangman, Number Prediction), Quran app, and a full-stack ecommerce app with Google Auth, seller dashboard, and self-hosted database.}
    \resumeItem{\textbf{Software Engineering Course at ALX:} Covered software engineering principles, full-stack development, and project management.}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  % \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{%
    \textbf{Languages:} C/C++, C\#, Python, JavaScript, Bash, SQL, Dart\\[3pt]
    \textbf{Frameworks:} Flutter, Next.js, FastAPI, .NET\\[3pt]
    \textbf{Developer Tools:} Git, SSH, Docker, CI/CD (GitHub Actions), self hosting services\\[3pt]
    \textbf{Database:} Postgres, MySQL, Supabase (Postgres + Blob Storage) \\[3pt]
    \textbf{LLM \& Agents:} Chat-based model integration, tools \& function calling, agentic workflows (routing, planning, retrieval), vector embeddings with LLMs (RAG-style), LangChain, MCP-based tool integration

  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
